---
title: "Wine Analysis"
author: "Sushmitha K"
date: "April 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("E:/Extra/Wine ratings")
wine <- read.csv("winemag-data_first150k.csv",stringsAsFactors = F,encoding = "UTF-8")
library(dplyr)
library(ggplot2)
library(knitr)
```

#Exploring Wine Ratings data set using EDA techiniques by using following packages

- dplyr
- ggplot2


###Dropping 2 unwanted columns

```{r}
wine <- wine[,-c(1,3)]

```
###total number of wines per country
###grouping by countries and then finding the count 

```{r message=FALSE, warning=FALSE}
countries_count = wine %>% group_by(country) %>% summarise(count = n()) %>% arrange(desc(count))
```


###top 10 mass producing countries
###grouping by countries and then finding the count ,arranging them in decending order and finding the top 10 countries

```{r}
selected_countries = wine %>% group_by(country) %>% summarise(count = n()) %>% arrange(desc(count)) %>% top_n(10) %>% select(country)
kable(selected_countries)

kable(class(selected_countries))
```


###converting the single column data frame into a vector

```{r}
selected_countries = as.character(selected_countries$country)
kable(class(selected_countries))
```


###average points of top 10 mass producing countries
###filtering top 10 countries and displaying their average points

```{r}
select_avg_point = wine %>%group_by(country) %>% filter(country %in% selected_countries)%>% summarize(avg_points = mean(points))%>%arrange(desc(avg_points))%>% head(10)

```

#points of top 10 mass producing countries
#filtering top 10 countries and displaying their points
```{r}
select_point = wine %>% filter(country %in% selected_countries) %>% select(country,points) %>% arrange(country)
```


###To find if points and price are correlated 

```{r message=FALSE, warning=FALSE}

ggplot(wine,aes(points,price)) + geom_point() + geom_smooth()
```


###Distribution of top 10 wine producing countries wrt points

```{r}
ggplot(select_point,aes(x = reorder(country,points,median),y = points)) +geom_boxplot(aes(fill = country)) +xlab("country") +ylab("points") +ggtitle("Distribution of top 10 wine producing countries") + theme(plot.title = element_text(hjust = .5))
```


###Other top 10 producers of large quantity but low quality

```{r}

kable(wine %>% filter(!(country %in% selected_countries)) %>% group_by(country) %>% summarise(median = median(points))%>% arrange(desc(median)))
```


###Top countries with high points 

```{r}
top = wine %>% group_by(country) %>% summarise(median = median(points)) %>% arrange(desc(median))
kable(top)
top = as.character(top$country)
```


###Top countries which are both high quantity and high quality
###10 countries both in selected countries and top list

```{r}
both = intersect(top,selected_countries)
kable(both)
```


###Top 10 high quality

```{r}
top = top[1:10]
kable(top)
```


###Top countries which are both high quantity and high quality

```{r}
both = intersect(top,selected_countries)
kable(both)
```


###Top countries which are both high quantity or high quality

```{r}
not = setdiff(top,selected_countries)
kable(not)
```


###Grouping wrt the type of grapes

```{r}
topwine = wine %>% group_by(variety) %>% summarise(number = n()) %>% arrange(desc(number)) %>% head(10)
kable(topwine)
```


###Convert to a character vector

```{r}
topwine = as.character(topwine$variety)
```


###Top 10 varieties with high points

```{r}
wine %>% filter(variety %in% topwine) %>% group_by(variety) %>% summarise(median = median(points)) %>% ggplot(aes(x = reorder(variety,median),y = median)) + geom_col(aes(fill = variety)) +xlab("variety") +ylab("Median Point") +scale_x_discrete(labels = abbreviate)
```


###Highly rated but low cost

```{r}
top15p = wine %>% arrange(desc(points)) %>% filter(points > quantile(points,prob = .85))

cheapest15p = wine %>% arrange(price) %>% head(nrow(top15p)) 


goodvalue = intersect(top15p,cheapest15p)
kable(goodvalue$country)

```

###Creating new column by using mutate
###Adding a new column called PPratio ,ie points to price ratio tp the existing data frame

```{r}
wine = wine %>% mutate(ppratio = points/price)

```

###Transmute
###Creates new data frame with only the newly created column

```{r}
wine1 = wine %>% transmute(ppratio = points/price)

```


###Data imputation

```{r}
wine %>% group_by(country)%>% summarise(total = n())

wine[wine$country == "",]#displaying all the rows which have no values

# wine$country =ifelse(wine$designation == "Askitikos","Greece",wine$country)

# wine$country =ifelse(wine$designation == "Piedra Feliz","Chile",wine$country)

# wine$country =ifelse(wine$winery == "Büyülübag","Turkey",wine$country)

#or

# wine$country =ifelse(wine$X == 1440 , "Turkey",wine$country)

```


###Joining 2 datasets
```{r}
newwine = wine %>% group_by(country) %>% summarise(total = n()) %>% arrange(desc(total)) %>% arrange(desc(total))

subset1 = head(wine)

subset2 = head(newwine)

### full joint
full = full_join(subset1,subset2)

full

###inner joint
inner = inner_join(subset1,subset2)

inner


###left joint
left = left_join(subset1,subset2)

left

###right joint
right = right_join(subset1,subset2)

right
```

